---
title: "Colors"
output: html_document
date: "`r Sys.Date()`"
---

* library(ggplot2)\
* library(RColorBrewer)\
* library(viridis)\
* library(colorspace)\
* library(wesanderson)\
* library(yarrr)\
* library(ghibli)\
* library(dutchmasters) #(devtools::install_github("EdwinTh/dutchmasters"))\
* library(ochRe) #(devtools::install_github("ropenscilabs/ochRe"))\

```{r include=FALSE}
library(ggplot2)
library(RColorBrewer)
library(viridis)
library(colorspace)
library(wesanderson)
library(yarrr)
library(ghibli)
library(dutchmasters)
library(remotes)
library(ochRe)
library(scales)
library(ggsci)
library(gridExtra)
```

A simple guide to show a selection of color schemes and palettes available in R

## Color Theory

### Selecting Colors

* All functions below are taken from: https://github.com/gastonstat/colortools 
* This library has been removed from R - but functions can be taken from the github link above

```{r include=FALSE}
# source: https://github.com/gastonstat/colortools 
adjacent <-
function(color, plot=TRUE, bg="white", labcol=NULL, cex=0.8, title=TRUE)
{	
	tmp_cols = setColors(color, 12)
	adja_colors <- tmp_cols[c(1,2,12)]

	# plot
	if (plot)
	{
		# labels color
		if (is.null(labcol)) 
		{
			lab_col = rep("", 12)
			if (mean(col2rgb(bg)) > 127)
			{
				lab_col[c(1, 2, 12)] <- "black"
				lab_col[c(3:11)] <- col2HSV(bg)
			} else {
				lab_col[c(1, 2, 12)] <- "white"
				lab_col[c(3:11)] <- col2HSV(bg)
			}
		} else {
			lab_col = rep(labcol, 12)
			if (mean(col2rgb(bg)) > 127)
			{
				lab_col[c(1, 2, 12)] <- labcol
				lab_col[c(3:11)] <- col2HSV(bg)
			} else {
				lab_col[c(1, 2, 12)] <- labcol
				lab_col[c(3:11)] <- col2HSV(bg)
			}
		}	
		# hide non-adjacent colors
		tmp_cols[c(3:11)] <- paste(substr(tmp_cols[c(3:11)],1,7), "0D", sep="")
		pizza(tmp_cols, labcol=lab_col, bg=bg, cex=cex)
		# title
		if (title)
			title(paste("Adjacent (analogous) colors of: ", tmp_cols[1]), 
				col.main=lab_col[1], cex.main=0.8)
	}
	# result
	adja_colors
}
```

```{r include=FALSE}
# source: https://github.com/gastonstat/colortools 
anagrams <-
function(color)
{
	# convert to HSV
	col_hsv = rgb2hsv(col2rgb((color)))[,1]
	# get hue, saturation, and value
	hue = col_hsv[1]
	sat = col_hsv[2]
	val = col_hsv[3]
	# transparency
	alpha = 1
	if (substr(color, 1, 1) == "#" && nchar(color) == 9)
		alpha = substr(color, 8, 9)
	# make sure it is in HEX code
	hex = hsv(hue, sat, val)
	# break down hex in pairs
	par1 = substr(hex, 2, 3)
	par2 = substr(hex, 4, 5)
	par3 = substr(hex, 6, 7)
	# put pars in a vector
	hp = c(par1, par2, par3)
	# create vector to store results
	anacols = rep("", 27)
	# generate anagrams
	aux = 1
	for (i in 1:3)
	{
		for (j in 1:3)
		{
			for (k in 1:3)
			{
				anacols[aux] = paste("#", hp[i], hp[j], hp[k], sep="")
				aux = aux + 1
			}
		}
	}
	if (alpha != 1)
		anacols = paste(anacols, alpha, sep="")
	# result
	anacols
}
```

```{r include=FALSE}
# source: https://github.com/gastonstat/colortools 
analogous <-
function(color, plot=TRUE, bg="white", labcol=NULL, cex=0.8, title=TRUE) 
{
	adjacent(color, plot=plot, bg=bg, labcol=labcol, cex=cex, title=title)
}
```

```{r include=FALSE}
# source: https://github.com/gastonstat/colortools 
col2HSV <-
function(color)
{
	# convert to RGB
	rgb_col = col2rgb(color)
	# convert to HSV
	hsv_col = rgb2hsv(rgb_col)
	if (length(color) == 1)
	{
		# get degree
		hue = hsv_col[1]
		sat = hsv_col[2]
		val = hsv_col[3]
		# get colors with hsv
		hex_col = hsv(hue, sat, val)
	}
	if (length(color) > 1)
	{
		hex_col = rep("", length(color))
		for (j in 1:length(color))
		{
			hex_col[j] = hsv(hsv_col[1,j], hsv_col[2,j], hsv_col[3,j])
		}
	}
	hex_col
}
```

```{r include=FALSE}
# source: https://github.com/gastonstat/colortools 
complementary <-
function(color, plot=TRUE, bg="white", labcol=NULL, cex=0.8, title=TRUE)
{	
	tmp_cols = setColors(color, 12)
	comp_colors <- tmp_cols[c(1, 7)]

	# plot
	if (plot)
	{
		# labels color
		if (is.null(labcol)) 
		{
			lab_col = rep("", 12)
			if (mean(col2rgb(bg)) > 127)
			{
				lab_col[c(1, 7)] <- "black"
				lab_col[c(2:6,8:12)] <- col2HSV(bg)
			} else {
				lab_col[c(1, 7)] <- "white"
				lab_col[c(2:6,8:12)] <- col2HSV(bg)
			}
		} else {
			lab_col = rep(labcol, 12)
			if (mean(col2rgb(bg)) > 127)
			{
				lab_col[c(1, 7)] <- labcol
				lab_col[c(2:6,8:12)] <- col2HSV(bg)
			} else {
				lab_col[c(1, 7)] <- labcol
				lab_col[c(2:6,8:12)] <- col2HSV(bg)
			}
		}	
		# hide non-adjacent colors
		tmp_cols[c(2:6,8:12)] <- paste(substr(tmp_cols[c(2:6,8:12)],1,7), "0D", sep="")
		pizza(tmp_cols, labcol=lab_col, bg=bg, cex=cex)
		# title
		if (title)
			title(paste("Complementary (opposite) color of: ", tmp_cols[1]), 
				col.main=lab_col[1], cex.main=0.8)
	}
	# result
	comp_colors
}
```

```{r include=FALSE}
# source: https://github.com/gastonstat/colortools 
opposite <-
function(color, plot=TRUE, bg="white", labcol=NULL, cex=0.8, title=TRUE) 
{
	complementary(color, plot=plot, bg=bg, labcol=labcol, cex=cex, title=title)
}
```

```{r include=FALSE}
# source: https://github.com/gastonstat/colortools 
pizza <-
function(colors, bg = "gray95", border = NA, 
	init.angle = 105, cex = 0.8, lty = 1, labcol = NULL, ...)
{
  n <- length(colors)
  x <- rep(1, n)
  x <- c(0, cumsum(x)/sum(x))
  dx <- diff(x)
  nx <- length(dx)
  # set colors
  labels = colors
  # 
  if (is.null(labcol))
  {
    if (mean(col2rgb(bg)) > 127)
      labcol = rep("black", n)
    if (mean(col2rgb(bg)) <= 127)
      labcol = rep("white", n)
  }
  # prepare plot window
  par(bg = bg)
  plot.new()
  pin <- par("pin")
  xlim <- ylim <- c(-1, 1)
  if (pin[1L] > pin[2L]) 
    xlim <- (pin[1L]/pin[2L]) * xlim
  else ylim <- (pin[2L]/pin[1L]) * ylim
  dev.hold()
  on.exit(dev.flush())
  plot.window(xlim, ylim, "", asp = 1)
  # get ready to plot
  border <- rep(border, length.out = nx)
  if (is.null(border[1]))
    border <- rep(bg, length.out = nx)
  lty <- rep(lty, length.out = nx)
  angle <- rep(45, length.out = nx)
  radius = seq(1, 0, by=-1/n)[1:n]
  twopi <- -2 * pi
  t2xy <- function(t, rad) {
    t2p <- twopi * t + init.angle * pi/180
    list(x = rad * cos(t2p), y = rad * sin(t2p))
  }
  # plot colored segments
  for (i in 1L:nx)
  {
    n <- max(2, floor(200 * dx[i]))
    P <- t2xy(seq.int(x[i], x[i + 1], length.out = n), rad=radius[1])
    polygon(c(P$x, 0), c(P$y, 0), angle = angle[i], 
            border = border[i], col = colors[i], lty = lty[i])
    P <- t2xy(mean(x[i + 0:1]), rad=radius[1])
    lab <- labels[i]
    if (!is.na(lab) && nzchar(lab)) {
      adjs = 0.5
      if (P$x > 1e-08) adjs <- 0
      if (P$x < -1e-08) adjs <- 1
      lines(c(1, 1.05) * P$x, c(1, 1.05) * P$y, col=labcol[i])
      text(1.1 * P$x, 1.1 * P$y, labels[i], xpd = TRUE, 
           adj = adjs, cex=cex, col=labcol[i], ...)
    }
  }
  invisible(NULL)
}
```

```{r include=FALSE}
# source: https://github.com/gastonstat/colortools 
sequential <-
function(color, percentage=5, what="saturation", 
	s=NULL, v=NULL, alpha=NULL, fun="linear", plot=TRUE, verbose=TRUE)
{	
	# convert to HSV
	col_hsv = rgb2hsv(col2rgb(color))[,1]
	# transparency
	if (is.null(alpha))
		alpha = 1
	if (substr(color, 1, 1) == "#" && nchar(color) == 9)
		alpha = substr(color, 8, 9)
	# get hue, saturation, and value
	hue = col_hsv[1]
	if (is.null(s)) s = col_hsv[2]
	if (is.null(v)) v = col_hsv[3]
	# sequence function
	getseq = switch(fun, 
		linear = seq(0, 1, by=percentage/100),
		sqrt = sqrt(seq(0, 1, by=percentage/100)),
		log = log1p(seq(0, 1, by=percentage/100)),
		log10 = log10(seq(0, 1, by=percentage/100))
		)
	# what type of sequence?
	if (what == "saturation") {
		sat = getseq
		fixed = paste("v=", round(v,2), " and alpha=", alpha, sep="")
		if (is.numeric(alpha))
			seq_col = hsv(hue, s=sat, v=v, alpha=alpha)
		if (is.character(alpha)) {
			seq_col = hsv(hue, s=sat, v=v)
			seq_col = paste(seq_col, alpha, sep="")
		}
	}
	if (what == "value") {
		val = getseq
		fixed = paste("s=", round(s,2), " and alpha=", alpha, sep="")
		if (is.numeric(alpha))
			seq_col = hsv(hue, s=s, v=val, alpha=alpha)
		if (is.character(alpha)) {
			seq_col = hsv(hue, s=s, v=val)
			seq_col = paste(seq_col, alpha, sep="")
		}
	}
	if (what == "alpha") {
		alpha = getseq
		fixed = paste("s=", round(s,2), " and v=", round(v,2), sep="")
		seq_col = hsv(hue, s=s, v=v, alpha=alpha)
	}
	# if plot TRUE
	if (plot)
	{
		n = length(seq(0, 1, by=percentage/100))
		fx = unlist(fixed)
		#dev.new()
		plot(0, 0, type="n", xlim=c(0,1), ylim=c(0,1), axes=FALSE, xlab="", ylab="")
		rect(0:(n-1)/n, 0, 1:n/n, 1, col=seq_col, border="lightgray")
		mtext(seq_col, side=1, at=0.5:(n)/n, cex=0.8, las=2)
		title(paste("Sequential colors based on ", what, "\n with fixed ", fx, sep=""),
			cex.main=0.9)
	}
	# result
	if (verbose)
		seq_col
}
```

```{r include=FALSE}
# source: https://github.com/gastonstat/colortools 
setColors <-
function(color, num)
{
	# convert to RGB
	rgb_col = col2rgb(color)
	# convert to HSV
	hsv_col = rgb2hsv(rgb_col)[,1]
	# get degree
	hue = hsv_col[1]
	sat = hsv_col[2]
	val = hsv_col[3]
	cols = seq(hue, hue + 1, by=1/num)
	cols = cols[1:num]
	cols[cols > 1] <- cols[cols > 1] - 1
	# get colors with hsv
	colors = hsv(cols, sat, val)
	# transparency
	if (substr(color, 1, 1) == "#" && nchar(color) == 9)
	{
		alpha = substr(color, 8, 9)
		colors = paste(colors, alpha, sep="")
	}
	colors
}
```

```{r include=FALSE}
# source: https://github.com/gastonstat/colortools 
splitComp <-
function(color, plot=TRUE, bg="white", labcol=NULL, cex=0.8, title=TRUE)
{	
	tmp_cols = setColors(color, 12)
	split_colors <- tmp_cols[c(1,6,8)]

	# plot
	if (plot)
	{
		# labels color
		if (is.null(labcol)) 
		{
			lab_col = rep("", 12)
			if (mean(col2rgb(bg)) > 127)
			{
				lab_col[c(1, 6, 8)] <- "black"
				lab_col[c(2:5,7,9:12)] <- col2HSV(bg)
			} else {
				lab_col[c(1, 6, 8)] <- "white"
				lab_col[c(2:5,7,9:12)] <- col2HSV(bg)
			}
		} else {
			lab_col = rep(labcol, 12)
			if (mean(col2rgb(bg)) > 127)
			{
				lab_col[c(1, 6, 8)] <- labcol
				lab_col[c(2:5,7,9:12)] <- col2HSV(bg)
			} else {
				lab_col[c(1, 6, 8)] <- labcol
				lab_col[c(2:5,7,9:12)] <- col2HSV(bg)
			}
		}	
		# hide non-adjacent colors
		tmp_cols[c(2:5,7,9:12)] <- paste(substr(tmp_cols[c(2:5,7,9:12)],1,7), "0D", sep="")
		pizza(tmp_cols, labcol=lab_col, bg=bg, cex=cex)
		# title
		if (title)
			title(paste("Split complementary colors of: ", tmp_cols[1]), 
				col.main=lab_col[1], cex.main=0.8)
	}
	# result
	split_colors
}
```

```{r include=FALSE}
# source: https://github.com/gastonstat/colortools 
square <-
function(color, plot=TRUE, bg="white", labcol=NULL, cex = 0.8, title=TRUE)
{	
	tmp_cols = setColors(color, 12)
	sqr_colors <- tmp_cols[c(1,4,7,10)]

	# plot
	if (plot)
	{
		# labels color
		if (is.null(labcol)) 
		{
			lab_col = rep("", 12)
			if (mean(col2rgb(bg)) > 127)
			{
				lab_col[c(1,4,7,10)] <- "black"
				lab_col[c(2,3,5,6,8,9,11,12)] <- col2HSV(bg)
			} else {
				lab_col[c(1,4,7,10)] <- "white"
				lab_col[c(2,3,5,6,8,9,11,12)] <- col2HSV(bg)
			}
		} else {
			lab_col = rep(labcol, 12)
			if (mean(col2rgb(bg)) > 127)
			{
				lab_col[c(1,4,7,10)] <- labcol
				lab_col[c(2,3,5,6,8,9,11,12)] <- col2HSV(bg)
			} else {
				lab_col[c(1,4,7,10)] <- labcol
				lab_col[c(2,3,5,6,8,9,11,12)] <- col2HSV(bg)
			}
		}	
		# hide non-adjacent colors
		tmp_cols[c(2,3,5,6,8,9,11,12)] <- paste(substr(tmp_cols[c(2,3,5,6,8,9,11,12)],1,7), "0D", sep="")
		pizza(tmp_cols, labcol=lab_col, bg=bg, cex = cex)
		# title
		if (title)
			title(paste("Square color scheme of: ", tmp_cols[1]), 
				col.main=lab_col[1], cex.main=0.8)
	}
	# result
	sqr_colors
}
```

```{r include=FALSE}
# source: https://github.com/gastonstat/colortools 
tetradic <-
function(color, plot=TRUE, bg="white", labcol=NULL, cex=0.8, title=TRUE)
{	
	tmp_cols = setColors(color, 12)
	tetrad_colors <- tmp_cols[c(1,3,7,9)]

	# plot
	if (plot)
	{
		# labels color
		if (is.null(labcol)) 
		{
			lab_col = rep("", 12)
			if (mean(col2rgb(bg)) > 127)
			{
				lab_col[c(1,3,7,9)] <- "black"
				lab_col[c(2,4,5,6,8,10,11,12)] <- col2HSV(bg)
			} else {
				lab_col[c(1,3,7,9)] <- "white"
				lab_col[c(2,4,5,6,8,10,11,12)] <- col2HSV(bg)
			}
		} else {
			lab_col = rep(labcol, 12)
			if (mean(col2rgb(bg)) > 127)
			{
				lab_col[c(1,3,7,9)] <- labcol
				lab_col[c(2,4,5,6,8,10,11,12)] <- col2HSV(bg)
			} else {
				lab_col[c(1,3,7,9)] <- labcol
				lab_col[c(2,4,5,6,8,10,11,12)] <- col2HSV(bg)
			}
		}	
		# hide non-adjacent colors
		tmp_cols[c(2,4,5,6,8,10,11,12)] <- paste(substr(tmp_cols[c(2,4,5,6,8,10,11,12)],1,7), "0D", sep="")
		pizza(tmp_cols, labcol=lab_col, bg=bg, cex=cex)
		# title
		if (title)
			title(paste("Tetradic colors of: ", tmp_cols[1]), 
				col.main=lab_col[1], cex.main=0.8)
	}
	# result
	tetrad_colors
}
```

```{r include=FALSE}
# source: https://github.com/gastonstat/colortools 
triadic <-
function(color, plot=TRUE, bg="white", labcol=NULL, cex=0.8, title=TRUE)
{	
	tmp_cols = setColors(color, 12)
	triad_colors <- tmp_cols[c(1,5,9)]

	# plot
	if (plot)
	{
		# labels color
		if (is.null(labcol)) 
		{
			lab_col = rep("", 12)
			if (mean(col2rgb(bg)) > 127)
			{
				lab_col[c(1, 5, 9)] <- "black"
				lab_col[c(2,3,4,6,7,8,10,11,12)] <- col2HSV(bg)
			} else {
				lab_col[c(1, 5, 9)] <- "white"
				lab_col[c(2,3,4,6,7,8,10,11,12)] <- col2HSV(bg)
			}
		} else {
			lab_col = rep(labcol, 12)
			if (mean(col2rgb(bg)) > 127)
			{
				lab_col[c(1, 5, 9)] <- labcol
				lab_col[c(2,3,4,6,7,8,10,11,12)] <- col2HSV(bg)
			} else {
				lab_col[c(1, 5, 9)] <- labcol
				lab_col[c(2,3,4,6,7,8,10,11,12)] <- col2HSV(bg)
			}
		}
		# hide non-adjacent colors
		tmp_cols[c(2,3,4,6,7,8,10,11,12)] <- paste(
			substr(tmp_cols[c(2,3,4,6,7,8,10,11,12)],1,7), "0D", sep="")
		pizza(tmp_cols, labcol=lab_col, bg=bg, cex=cex)
		# title
		if (title)
			title(paste("Triadic color scheme of: ", tmp_cols[1]), 
				col.main=lab_col[1], cex.main=0.8)
	}
	# result
	triad_colors
}
```


```{r include=FALSE}
# source: https://github.com/gastonstat/colortools 
wheel <-
function(color, num=12, bg="gray95", border=NULL, 
	init.angle=105, cex=1, lty=NULL, main=NULL, verbose=TRUE, ...)
{
  if (!is.numeric(num) || any(is.na(num) | num < 0)) 
    stop("\n'num' must be positive")
  x <- rep(1, num)
  x <- c(0, cumsum(x)/sum(x))
  dx <- diff(x)
  nx <- length(dx)
  # set colors
  col = setColors(color, num)
  labels = col
  # labels color
  labcol = ifelse( mean(col2rgb(bg)) > 127, "black", "white")
  # prepare plot window
  par(bg = bg)
  plot.new()
  pin <- par("pin")
  xlim <- ylim <- c(-1, 1)
  if (pin[1L] > pin[2L]) 
    xlim <- (pin[1L]/pin[2L]) * xlim
  else ylim <- (pin[2L]/pin[1L]) * ylim
  dev.hold()
  on.exit(dev.flush())
  plot.window(xlim, ylim, "", asp = 1)
  # get ready to plot
  if (is.null(border[1])) {
    border <- rep(bg, length.out = nx)    
  } else {
    border <- rep(border, length.out = nx)    
  }
  if (!is.null(lty))
    lty <- rep(NULL, length.out = nx)
  angle <- rep(45, length.out = nx)
  radius = seq(1, 0, by=-1/num)[1:num]
  twopi <- -2 * pi
  t2xy <- function(t, rad) {
    t2p <- twopi * t + init.angle * pi/180
    list(x = rad * cos(t2p), y = rad * sin(t2p))
  }
  # plot colored segments
  for (i in 1L:nx)
  {
    n <- max(2, floor(200 * dx[i]))
    P <- t2xy(seq.int(x[i], x[i + 1], length.out = n), rad=radius[1])
    polygon(c(P$x, 0), c(P$y, 0), angle = angle[i], 
            border = border[i], col = col[i], lty = lty[i])
    P <- t2xy(mean(x[i + 0:1]), rad=radius[1])
    lab <- labels[i]
    if (!is.na(lab) && nzchar(lab)) {
      adjs = 0.5
      if (P$x > 1e-08) adjs <- 0
      if (P$x < -1e-08) adjs <- 1
      lines(c(1, 1.05) * P$x, c(1, 1.05) * P$y)
      text(1.1 * P$x, 1.1 * P$y, labels[i], xpd = TRUE, 
           adj = adjs, cex=cex, col=labcol, ...)
    }
  }
  # add title
  title(main = main, ...)
  # return color names
  if (verbose)
    col
}
```

```{r, echo=FALSE}
wheel("darkblue", num = 12)
adjacent("darkblue")
complementary("darkblue")
triadic("darkblue")
tetradic("darkblue")
square("darkblue")
splitComp("darkblue")
sequential("darkblue")
```

### Hue Saturation Value (HSV) = Hue Saturation Brightness (HSB) Colour Space 
* A colour can be specified using R's hsv() function that takes three arguments: hue, saturation, and value (brightness), all in the range [0, 1]

```{r, echo=FALSE}
d=expand.grid(h=seq(0,0.95,0.05), s=seq(0,0.95,0.05), v=seq(0,1,0.2))
ggplot() +
coord_polar(theta="x") +
facet_wrap(~v) +
scale_x_continuous(name="hue", limits=c(0,1), breaks=seq(0.025,0.925,0.1), labels=seq(0,0.9,0.1)) +
scale_y_continuous(name="saturation", breaks=seq(0, 1, 0.2)) +
scale_fill_identity() +
geom_rect(data=d, mapping=aes(xmin=h, xmax=h+resolution(h), ymin=s, ymax=s+resolution(s), fill=hsv(h,s,v)), color="white", linewidth=0.1)
```

### Hue Chroma Luminance (HCL) Colour Space
* A colour can be specified using R's hcl() function that takes three arguments: hue [0,360], chroma [0,100], and luminance [0,100]
* This space is similar to the HSV space, however, in the HCL space steps of equal size correspond to approximately equal perceptual changes in colour 
  + Note that the possible values of chroma and luminance actually depend on the specific hue; the ranges above are only indicative

```{r, echo=FALSE}
d=expand.grid(h=seq(0,350,10), c=seq(0,100,5), l=seq(0,100,20))
ggplot() +
coord_polar(theta="x")+facet_wrap(~l) +
scale_x_continuous(name="hue", limits=c(0,360), breaks=seq(5,345,20), labels=seq(0,340,20)) +
scale_y_continuous(name="chroma", breaks=seq(0, 100, 20)) +
scale_fill_identity() +
geom_rect(data=d, mapping=aes(xmin=h, xmax=h+resolution(h), ymin=c, ymax=c+resolution(c), fill=hcl(h,c,l)), color="white", linewidth=0.1)
```

### Red Green Blue (RGB) Colour Space
* RGB is the built-in colour space. Instead of "manually" creating a #RRGGBB colour string, a colour can be specified using R's rgb() function that takes three arguments: red, green, and blue (which, by default, all have a range of [0, 1])

```{r, echo=FALSE}
d=expand.grid(r=seq(0,1,0.1), g=seq(0,1,0.1), b=seq(0,1,0.1))
ggplot() +
facet_wrap(~b) +
scale_x_continuous(name="red", breaks=seq(0.05, 1.05, 0.2), labels=seq(0, 1, 0.2)) +
scale_y_continuous(name="green", breaks=seq(0.05, 1.05, 0.2), labels=seq(0, 1, 0.2)) +
scale_fill_identity() +
geom_rect(data=d, mapping=aes(xmin=r, xmax=r+resolution(r), ymin=g, ymax=g+resolution(g), fill=rgb(r,g,b)), color="white", linewidth=0.1)
```

## Color Palletes

### RColorBrewer

```{r, echo=FALSE}
display.brewer.all(type='seq')
```

```{r, echo=FALSE}
display.brewer.all(type='seq', colorblindFriendly = TRUE)
```

```{r, echo=FALSE}
display.brewer.all(type='qual')
```

```{r, echo=FALSE}
display.brewer.all(type='qual', colorblindFriendly = TRUE)
```

```{r, echo=FALSE}
display.brewer.all(type='div')
```

```{r, echo=FALSE}
display.brewer.all(type='div', colorblindFriendly = TRUE)
```

### Viridis

```{r, echo=FALSE}
viridis_names <-c("magma", "inferno", "plasma", "viridis", "cividis", "rocket", "mako", "turbo")

n <- 50
par(mfrow=c(8,1), mar = c(1,1,1,1))
f <- sapply(1:8, function(x) image(matrix(1:n, n, 1), col = viridis(n=n, option = LETTERS[x]), axes =FALSE, main = viridis_names[x]))
```

### colorspace

```{r, echo=FALSE}
hcl_palettes("qualitative", plot = TRUE)
hcl_palettes("sequential (single-hue)", plot = TRUE)
hcl_palettes("sequential (multi-hue)", plot = TRUE)
hcl_palettes("diverging", plot = TRUE)
```

### wesanderson

```{}
wes_palette(name, n, type = c("discrete", "continuous"))
```

* `name`: Name of desired palette
* `n`: Number of colors desired. Unfortunately most palettes now only have 4 or 5 colors
* `type`: Either “continuous” or “discrete”
  + Use continuous if you want to automatically interpolate between colours

```{r, echo=FALSE}
par(mfrow=c(10,1))
for(i in names(wes_palettes)) {
  print(wes_palette(i))
}

```

### Pirate Palette (yarrr)

```{r, echo=FALSE}
piratepal(palette = "all")
```

### ochRe

```{r include=FALSE}
vis_palette <-
  function(pal,
           ttl = deparse(substitute(pal)),
           num = length(pal)) {
    if (num <= 0)
      stop("'num' should be > 0")
    pal_func <- grDevices::colorRampPalette(pal)
    graphics::image(
      seq_len(num),
      1,
      as.matrix(seq_len(num)),
      col = pal_func(num),
      main = paste0(ttl),
      xlab = "",
      ylab = "",
      xaxt = "n",
      yaxt = "n",
      bty = "n"
    )
  }
```

```{r, echo=FALSE}
pal_names <- names(ochre_palettes)
par(mfrow=c(length(ochre_palettes)/2, 2), 
    lheight = 2, mar=rep(1, 4), adj = 0)
for (i in 1:length(ochre_palettes)){
    vis_palette(ochre_palettes[[i]], pal_names[i])
}
```

### Dutch Masters

```{r, echo=FALSE}
pal_names <- names(dutchmasters)
par(mfrow=c(length(dutchmasters)/2, 2), 
    lheight = 2, mar=rep(1, 4), adj = 0)
for (i in 1:length(dutchmasters)){
    vis_palette(dutchmasters[[i]], pal_names[i])
}
```

### Ghibli 

```{r, echo=FALSE}
par(mfrow=c(9,3))
for(i in names(ghibli_palettes)) {
  print(ghibli_palette(i))
}
```


### ggsci Colors

#### Discrete Colors

```{r, echo=FALSE}
show_col(pal_npg()(10))
```

```{r, echo=FALSE}
show_col(pal_aaas()(10))
```


```{r, echo=FALSE}
show_col(pal_nejm()(8))
```


```{r, echo=FALSE}
show_col(pal_lancet()(9))
```


```{r, echo=FALSE}
show_col(pal_jama()(7))
```



```{r, echo=FALSE}
show_col(pal_bmj()(9))
```


```{r, echo=FALSE}
show_col(pal_jco()(10))
```


```{r, echo=FALSE}
show_col(pal_ucscgb()(10))
```


```{r, echo=FALSE}
show_col(pal_d3()(10))
```


```{r, echo=FALSE}
show_col(pal_locuszoom()(7))
```


```{r, echo=FALSE}
show_col(pal_igv()(10))
```


```{r, echo=FALSE}
show_col(pal_cosmic()(10))
```


```{r, echo=FALSE}
show_col(pal_uchicago()(9))
```


```{r, echo=FALSE}
show_col(pal_startrek()(7))
```


```{r, echo=FALSE}
show_col(pal_tron()(7))
```


```{r, echo=FALSE}
show_col(pal_futurama()(10))
```


```{r, echo=FALSE}
show_col(pal_rickandmorty()(10))
```


```{r, echo=FALSE}
show_col(pal_simpsons()(10))
```


```{r, echo=FALSE}
show_col(pal_flatui()(10))
```


```{r, echo=FALSE}
show_col(pal_frontiers()(10))
```


```{r, echo=FALSE}
show_col(pal_gsea()(10))
```


```{r, echo=FALSE}
show_col(pal_material()(10))
```


#### Continuous Colors

```{r, echo=FALSE, fig.height=1.2, fig.width=7}
# Define the palettes we want to use
ggsci_palettes <- list(
  GSEA = pal_gsea()(12)
)

# Set up the plotting area
n <- 12
par(mfrow = c(length(ggsci_palettes), 1), mar = c(1, 1, 1, 1))

# Create a function to plot each palette
plot_palette <- function(palette_name) {
  colors <- ggsci_palettes[[palette_name]]
  image(matrix(1:n, n, 1), col = colors, axes = FALSE, main = palette_name)
}

# Apply the function to each palette
invisible(sapply(names(ggsci_palettes), plot_palette))
```

```{r, echo=FALSE}
# Define the palettes
ggsci_palettes <- list(
  Bootstrap5_blue = pal_bs5("blue")(10),
  Bootstrap5_indigo = pal_bs5("indigo")(10),
  Bootstrap5_purple = pal_bs5("purple")(10),
  Bootstrap5_pink = pal_bs5("pink")(10)
)

# Set up the plotting area
n <- 10
par(mfrow = c(length(ggsci_palettes), 1), mar = c(1, 1, 1, 1))

# Create a function to plot each palette
plot_palette <- function(palette_name) {
  colors <- ggsci_palettes[[palette_name]]
  image(matrix(1:n, n, 1), col = colors, axes = FALSE, main = palette_name)
}

# Apply the function to each palette
invisible(sapply(names(ggsci_palettes), plot_palette))
```

```{r, echo=FALSE}
# Define the palettes
ggsci_palettes <- list(
  Bootstrap5_red = pal_bs5("red")(10),
  Bootstrap5_orange = pal_bs5("orange")(10),
  Bootstrap5_yellow = pal_bs5("yellow")(10)
)

# Set up the plotting area
n <- 10
par(mfrow = c(length(ggsci_palettes), 1), mar = c(1, 1, 1, 1))

# Create a function to plot each palette
plot_palette <- function(palette_name) {
  colors <- ggsci_palettes[[palette_name]]
  image(matrix(1:n, n, 1), col = colors, axes = FALSE, main = palette_name)
}

# Apply the function to each palette
invisible(sapply(names(ggsci_palettes), plot_palette))
```

```{r, echo=FALSE}
# Define the palettes
ggsci_palettes <- list(
  Bootstrap5_green = pal_bs5("green")(10),
  Bootstrap5_teal = pal_bs5("teal")(10),
  Bootstrap5_cyan = pal_bs5("cyan")(10),
  Bootstrap5_gray = pal_bs5("gray")(10)
)

# Set up the plotting area
n <- 10
par(mfrow = c(length(ggsci_palettes), 1), mar = c(1, 1, 1, 1))

# Create a function to plot each palette
plot_palette <- function(palette_name) {
  colors <- ggsci_palettes[[palette_name]]
  image(matrix(1:n, n, 1), col = colors, axes = FALSE, main = palette_name)
}

# Apply the function to each palette
invisible(sapply(names(ggsci_palettes), plot_palette))
```


```{r, echo=FALSE}
# Define the palettes
ggsci_palettes <- list(
  Material_red = pal_material("red")(10),
  Material_pink = pal_material("pink")(10),
  Material_purple = pal_material("purple")(10),
  Material_deep_purple = pal_material("deep-purple")(10)
)

# Set up the plotting area
n <- 10
par(mfrow = c(length(ggsci_palettes), 1), mar = c(1, 1, 1, 1))

# Create a function to plot each palette
plot_palette <- function(palette_name) {
  colors <- ggsci_palettes[[palette_name]]
  image(matrix(1:n, n, 1), col = colors, axes = FALSE, main = palette_name)
}

# Apply the function to each palette
invisible(sapply(names(ggsci_palettes), plot_palette))
``` 

```{r, echo=FALSE}
# Define the palettes
ggsci_palettes <- list(
  Material_indigo = pal_material("indigo")(10),
  Material_blue = pal_material("blue")(10),
  Material_light_blue = pal_material("light-blue")(10),
  Material_cyan = pal_material("cyan")(10)
)

# Set up the plotting area
n <- 10
par(mfrow = c(length(ggsci_palettes), 1), mar = c(1, 1, 1, 1))

# Create a function to plot each palette
plot_palette <- function(palette_name) {
  colors <- ggsci_palettes[[palette_name]]
  image(matrix(1:n, n, 1), col = colors, axes = FALSE, main = palette_name)
}

# Apply the function to each palette
invisible(sapply(names(ggsci_palettes), plot_palette))
``` 

```{r, echo=FALSE}
# Define the palettes
ggsci_palettes <- list(
  Material_teal = pal_material("teal")(10),
  Material_green = pal_material("green")(10),
  Material_light_green = pal_material("light-green")(10),
  Material_lime = pal_material("lime")(10)
)

# Set up the plotting area
n <- 10
par(mfrow = c(length(ggsci_palettes), 1), mar = c(1, 1, 1, 1))

# Create a function to plot each palette
plot_palette <- function(palette_name) {
  colors <- ggsci_palettes[[palette_name]]
  image(matrix(1:n, n, 1), col = colors, axes = FALSE, main = palette_name)
}

# Apply the function to each palette
invisible(sapply(names(ggsci_palettes), plot_palette))
``` 

```{r, echo=FALSE}
# Define the palettes
ggsci_palettes <- list(
  Material_yellow = pal_material("yellow")(10),
  Material_amber = pal_material("amber")(10),
  Material_orange = pal_material("orange")(10),
  Material_deep_orange = pal_material("deep-orange")(10)
)

# Set up the plotting area
n <- 10
par(mfrow = c(length(ggsci_palettes), 1), mar = c(1, 1, 1, 1))

# Create a function to plot each palette
plot_palette <- function(palette_name) {
  colors <- ggsci_palettes[[palette_name]]
  image(matrix(1:n, n, 1), col = colors, axes = FALSE, main = palette_name)
}

# Apply the function to each palette
invisible(sapply(names(ggsci_palettes), plot_palette))
``` 

```{r, echo=FALSE}
# Define the palettes
ggsci_palettes <- list(
  Material_brown = pal_material("brown")(10),
  Material_grey = pal_material("grey")(10),
  Material_blue_grey = pal_material("blue-grey")(10)
)

# Set up the plotting area
n <- 10
par(mfrow = c(length(ggsci_palettes), 1), mar = c(1, 1, 1, 1))

# Create a function to plot each palette
plot_palette <- function(palette_name) {
  colors <- ggsci_palettes[[palette_name]]
  image(matrix(1:n, n, 1), col = colors, axes = FALSE, main = palette_name)
}

# Apply the function to each palette
invisible(sapply(names(ggsci_palettes), plot_palette))
```

```{r, echo=FALSE}
# Define the palettes
ggsci_palettes <- list(
  Tailwind_slate = pal_tw3("slate")(10),
  Tailwind_gray = pal_tw3("gray")(10),
  Tailwind_zinc = pal_tw3("zinc")(10),
  Tailwind_neutral = pal_tw3("neutral")(10),
  Tailwind_stone = pal_tw3("stone")(10)
)

# Set up the plotting area
n <- 10
par(mfrow = c(length(ggsci_palettes), 1), mar = c(1, 1, 1, 1))

# Create a function to plot each palette
plot_palette <- function(palette_name) {
  colors <- ggsci_palettes[[palette_name]]
  image(matrix(1:n, n, 1), col = colors, axes = FALSE, main = palette_name)
}

# Apply the function to each palette
invisible(sapply(names(ggsci_palettes), plot_palette))
``` 

```{r, echo=FALSE}
# Define the palettes
ggsci_palettes <- list(
  Tailwind_red = pal_tw3("red")(10),
  Tailwind_orange = pal_tw3("orange")(10),
  Tailwind_amber = pal_tw3("amber")(10),
  Tailwind_yellow = pal_tw3("yellow")(10),
  Tailwind_lime = pal_tw3("lime")(10)
)

# Set up the plotting area
n <- 10
par(mfrow = c(length(ggsci_palettes), 1), mar = c(1, 1, 1, 1))

# Create a function to plot each palette
plot_palette <- function(palette_name) {
  colors <- ggsci_palettes[[palette_name]]
  image(matrix(1:n, n, 1), col = colors, axes = FALSE, main = palette_name)
}

# Apply the function to each palette
invisible(sapply(names(ggsci_palettes), plot_palette))
``` 

```{r, echo=FALSE}
# Define the palettes
ggsci_palettes <- list(
  Tailwind_green = pal_tw3("green")(10),
  Tailwind_emerald = pal_tw3("emerald")(10),
  Tailwind_teal = pal_tw3("teal")(10),
  Tailwind_cyan = pal_tw3("cyan")(10)
)

# Set up the plotting area
n <- 10
par(mfrow = c(length(ggsci_palettes), 1), mar = c(1, 1, 1, 1))

# Create a function to plot each palette
plot_palette <- function(palette_name) {
  colors <- ggsci_palettes[[palette_name]]
  image(matrix(1:n, n, 1), col = colors, axes = FALSE, main = palette_name)
}

# Apply the function to each palette
invisible(sapply(names(ggsci_palettes), plot_palette))
``` 

 
```{r, echo=FALSE}
# Define the palettes
ggsci_palettes <- list(
  Tailwind_sky = pal_tw3("sky")(10),
  Tailwind_blue = pal_tw3("blue")(10),
  Tailwind_indigo = pal_tw3("indigo")(10),
  Tailwind_violet = pal_tw3("violet")(10)
)

# Set up the plotting area
n <- 10
par(mfrow = c(length(ggsci_palettes), 1), mar = c(1, 1, 1, 1))

# Create a function to plot each palette
plot_palette <- function(palette_name) {
  colors <- ggsci_palettes[[palette_name]]
  image(matrix(1:n, n, 1), col = colors, axes = FALSE, main = palette_name)
}

# Apply the function to each palette
invisible(sapply(names(ggsci_palettes), plot_palette))
``` 

```{r, echo=FALSE}
# Define the palettes
ggsci_palettes <- list(
  Tailwind_purple = pal_tw3("purple")(10),
  Tailwind_fuschia = pal_tw3("fuchsia")(10),
  Tailwind_pink = pal_tw3("pink")(10),
  Tailwind_rose = pal_tw3("rose")(10)
)

# Set up the plotting area
n <- 10
par(mfrow = c(length(ggsci_palettes), 1), mar = c(1, 1, 1, 1))

# Create a function to plot each palette
plot_palette <- function(palette_name) {
  colors <- ggsci_palettes[[palette_name]]
  image(matrix(1:n, n, 1), col = colors, axes = FALSE, main = palette_name)
}

# Apply the function to each palette
invisible(sapply(names(ggsci_palettes), plot_palette))
``` 

### R inbuilt Colors

##### Standalones

```{r, echo=FALSE}
ran1 <- c("white", "floralwhite",  "ghostwhite", "mintcream", "whitesmoke", 
          "aliceblue", "cornflowerblue", "darkblue", "darkcyan", "darkturquoise", 
          "mediumblue", "navy", "navyblue", "mediumturquoise", "midnightblue", 
          "powderblue", "black", "darkslategrey", "beige",  "blanchedalmond",
          "papayawhip", "moccasin", "peru", "saddlebrown", "sandybrown")
ran2 <- c("blueviolet", "darkmagenta", "darkslateblue","darkviolet", "lavender", 
          "lightslateblue", "mediumslateblue", "mediumvioletred", "violet", "darkred",
          "darkgray", "darkgrey", "dimgray", "dimgrey", "gainsboro", 
          "lightgray", "lightgrey", "lightslategray", "lightslategrey", "slategrey")
ran3 <- c("darkgreen", "forestgreen", "greenyellow",  "lawngreen", "lightgreen",
          "lightseagreen", "limegreen", "mediumaquamarine", "mediumseagreen",  "mediumspringgreen", 
          "yellowgreen", "darkkhaki",  "darksalmon", "lightcoral", "lightgoldenrodyellow", "linen", "oldlace",
          "palegoldenrod")

show_col(ran1, cex_label = 0.6, ncol=5)
show_col(ran2, cex_label = 0.6, ncol=5)
show_col(ran3, cex_label = 0.6, ncol=5)
```

##### Green

```{r, echo=FALSE}
green1 <- c("aquamarine", "aquamarine1", "aquamarine2", "aquamarine3", "aquamarine4",
            "chartreuse", "chartreuse1", "chartreuse2", "chartreuse3", "chartreuse4",
            "darkolivegreen", "darkolivegreen1", "darkolivegreen2", "darkolivegreen3", "darkolivegreen4",
            "darkseagreen", "darkseagreen1", "darkseagreen2", "darkseagreen3", "darkseagreen4",
            "honeydew", "honeydew1", "honeydew2", "honeydew3", "honeydew4")
green2 <- c("olivedrab", "olivedrab1", "olivedrab2", "olivedrab3", "olivedrab4",
            "palegreen", "palegreen1", "palegreen2", "palegreen3", "palegreen4", 
            "seagreen", "seagreen1", "seagreen2", "seagreen3", "seagreen4",
            "springgreen", "springgreen1", "springgreen2", "springgreen3", "springgreen4")
show_col(green1, cex_label = 0.6, ncol=5)
show_col(green2, cex_label = 0.6, ncol=5)
```

##### Blue

```{r, echo=FALSE}
blue1 <- c("azure", "azure1", "azure2", "azure3", "azure4",
           "blue", "blue1", "blue2", "blue3", "blue4",
           "cadetblue", "cadetblue1", "cadetblue2", "cadetblue3", "cadetblue4",
           "cyan", "cyan1", "cyan2", "cyan3", "cyan4",
           "darkslategray", "darkslategray1", "darkslategray2", "darkslategray3", "darkslategray4"
)

blue2 <- c("deepskyblue", "deepskyblue1", "deepskyblue2", "deepskyblue3", "deepskyblue4",
           "dodgerblue", "dodgerblue1", "dodgerblue2", "dodgerblue3", "dodgerblue4",
           "lightblue", "lightblue1", "lightblue2", "lightblue3", "lightblue4", 
           "lightcyan", "lightcyan1", "lightcyan2", "lightcyan3", "lightcyan4"
)

blue3 <- c("lightskyblue", "lightskyblue1", "lightskyblue2", "lightskyblue3", "lightskyblue4",
           "lightsteelblue", "lightsteelblue1", "lightsteelblue2", "lightsteelblue3", "lightsteelblue4",
           "paleturquoise", "paleturquoise1", "paleturquoise2", "paleturquoise3", "paleturquoise4",
           "royalblue", "royalblue1", "royalblue2", "royalblue3", "royalblue4"
)

blue4 <- c("slategray", "slategray1", "slategray2", "slategray3", "slategray4",
           "skyblue", "skyblue1", "skyblue2", "skyblue3", "skyblue4",
           "steelblue", "steelblue1", "steelblue2", "steelblue3", "steelblue4",
           "turquoise", "turquoise1", "turquoise2", "turquoise3", "turquoise4"
)

show_col(blue1, cex_label = 0.6, ncol=5)
show_col(blue2, cex_label = 0.6, ncol=5)
show_col(blue3, cex_label = 0.6, ncol=5)
show_col(blue4, cex_label = 0.6, ncol=5)
```

##### Brown

```{r, echo=FALSE}
brown1 <- c("brown", "brown1", "brown2", "brown3", "brown4",
            "burlywood", "burlywood1", "burlywood2", "burlywood3", "burlywood4",
            "chocolate", "chocolate1", "chocolate2", "chocolate3", "chocolate4",
            "khaki", "khaki1", "khaki2", "khaki3", "khaki4"
)

brown2 <- c("sienna", "sienna1", "sienna2", "sienna3", "sienna4", 
            "tan", "tan1", "tan2", "tan3", "tan4",
            "wheat", "wheat1", "wheat2", "wheat3", "wheat4"
)
show_col(brown1, cex_label = 0.6, ncol=5)
show_col(brown2, cex_label = 0.6, ncol=5)
```

##### Yellow

```{r, echo=FALSE}
yellow1 <- c("darkgoldenrod", "darkgoldenrod1", "darkgoldenrod2", "darkgoldenrod3", "darkgoldenrod4",
             "gold", "gold1", "gold2", "gold3", "gold4", 
             "goldenrod", "goldenrod1", "goldenrod2", "goldenrod3", "goldenrod4",
             "lemonchiffon", "lemonchiffon1", "lemonchiffon2", "lemonchiffon3", "lemonchiffon4"
)
yellow2 <- c("lightgoldenrod", "lightgoldenrod1", "lightgoldenrod2", "lightgoldenrod3", "lightgoldenrod4", 
             "lightyellow", "lightyellow1", "lightyellow2", "lightyellow3", "lightyellow4",
             "yellow", "yellow1", "yellow2", "yellow3", "yellow4"
)
show_col(yellow1, cex_label = 0.6, ncol=5)
show_col(yellow2, cex_label = 0.6, ncol=5)
```

##### Orange

```{r, echo=FALSE}
orange1 <- c("bisque", "bisque1", "bisque2", "bisque3", "bisque4",
             "coral", "coral1", "coral2", "coral3", "coral4",
             "darkorange", "darkorange1", "darkorange2", "darkorange3", "darkorange4",
             "lightsalmon", "lightsalmon1", "lightsalmon2", "lightsalmon3", "lightsalmon4"
)

orange2 <- c("orange", "orange1", "orange2", "orange3", "orange4", 
             "orangered", "orangered1", "orangered2", "orangered3", "orangered4",
             "peachpuff", "peachpuff1", "peachpuff2", "peachpuff3", "peachpuff4",
             "salmon", "salmon1", "salmon2", "salmon3", "salmon4"
)
show_col(orange1, cex_label = 0.6, ncol=5)
show_col(orange2, cex_label = 0.6, ncol=5)
```

##### Red

```{r, echo=FALSE}
reds <- c("firebrick", "firebrick1", "firebrick2", "firebrick3", "firebrick4",
          "indianred", "indianred1", "indianred2", "indianred3", "indianred4",
          "red", "red1", "red2", "red3", "red4",
          "tomato", "tomato1", "tomato2", "tomato3", "tomato4"
)
show_col(reds, cex_label = 0.6, ncol=5)
```

##### Pink

```{r, echo=FALSE}
pink1 <- c("deeppink", "deeppink1", "deeppink2", "deeppink3", "deeppink4",
           "hotpink", "hotpink1", "hotpink2", "hotpink3", "hotpink4",
           "lightpink", "lightpink1", "lightpink2", "lightpink3", "lightpink4",
           "mistyrose", "mistyrose1", "mistyrose2", "mistyrose3", "mistyrose4"
)

pink2 <- c("pink", "pink1", "pink2", "pink3", "pink4",
           "rosybrown", "rosybrown1", "rosybrown2", "rosybrown3", "rosybrown4",
           "violetred", "violetred1", "violetred2", "violetred3", "violetred4"
)
show_col(pink1, cex_label = 0.6, ncol=5)
show_col(pink2, cex_label = 0.6, ncol=5)
```

##### Purple

```{r, echo=FALSE}
purple1 <- c("darkorchid", "darkorchid1", "darkorchid2", "darkorchid3", "darkorchid4",
             "lavenderblush", "lavenderblush1", "lavenderblush2", "lavenderblush3", "lavenderblush4",
             "magenta", "magenta1", "magenta2", "magenta3", "magenta4", 
             "maroon", "maroon1", "maroon2", "maroon3", "maroon4"
)
purple2 <- c("mediumorchid", "mediumorchid1", "mediumorchid2", "mediumorchid3", "mediumorchid4",
             "mediumpurple", "mediumpurple1", "mediumpurple2", "mediumpurple3", "mediumpurple4",
             "orchid", "orchid1", "orchid2", "orchid3", "orchid4", 
             "palevioletred", "palevioletred1", "palevioletred2", "palevioletred3", "palevioletred4"
)
purple3 <- c("purple", "purple1", "purple2", "purple3", "purple4",
             "plum", "plum1", "plum2", "plum3", "plum4",
             "slateblue", "slateblue1", "slateblue2", "slateblue3", "slateblue4",
             "thistle", "thistle1", "thistle2", "thistle3", "thistle4"
)
show_col(purple1, cex_label = 0.6, ncol=5)
show_col(purple2, cex_label = 0.6, ncol=5)
show_col(purple3, cex_label = 0.6, ncol=5)
```

##### Gray / Grey

```{r, echo=FALSE}
gray1 <- c("gray", "gray0", "gray1", "gray2", "gray3",
           "gray4", "gray5", "gray6", "gray7", "gray8", 
           "gray9", "gray10", "gray11", "gray12",  "gray13",
           "gray14", "gray15", "gray16", "gray17", "gray18",
           "gray19", "gray20", "gray21", "gray22", "gray23"
)
gray2 <- c("gray24", "gray25", "gray26", "gray27", "gray28",
           "gray29", "gray30", "gray31", "gray32", "gray33", 
           "gray34", "gray35", "gray36", "gray37", "gray38",
           "gray39", "gray40", "gray41", "gray42", "gray43", 
           "gray44", "gray45", "gray46", "gray47", "gray48"
)
gray3 <- c("gray49", "gray50", "gray51", "gray52", "gray53", 
           "gray54", "gray55", "gray56", "gray57", "gray58", 
           "gray59", "gray60", "gray61", "gray62", "gray63", 
           "gray64", "gray65", "gray66", "gray67", "gray68", 
           "gray69", "gray70", "gray71", "gray72", "gray73"
)
gray4 <- c("gray74", "gray75", "gray76", "gray77", "gray78", 
           "gray79", "gray80", "gray81", "gray82", "gray83", 
           "gray84", "gray85", "gray86", "gray87", "gray88", 
           "gray89", "gray90", "gray91", "gray92", "gray93"
)
gray5 <- c("gray94", "gray95", "gray96", "gray97", "gray98", 
           "gray99", "gray100"
)

show_col(gray1, cex_label = 0.6, ncol=5)
show_col(gray2, cex_label = 0.6, ncol=5)
show_col(gray3, cex_label = 0.6, ncol=5)
show_col(gray4, cex_label = 0.6, ncol=5)
show_col(gray5, cex_label = 0.6, ncol=5)
```

```{r, echo=FALSE}
grey1 <- c("grey", "grey0", "grey1", "grey2", "grey3", 
           "grey4","grey5", "grey6", "grey7", "grey8", 
           "grey9", "grey10", "grey11", "grey12", "grey13", 
           "grey14", "grey15", "grey16", "grey17", "grey18", 
           "grey19", "grey20", "grey21", "grey22", "grey23"
)
grey2 <- c("grey24", "grey25", "grey26", "grey27", "grey28", 
           "grey29", "grey30", "grey31", "grey32", "grey33", 
           "grey34", "grey35", "grey36", "grey37", "grey38", 
           "grey39", "grey40", "grey41", "grey42", "grey43", 
           "grey44", "grey45", "grey46", "grey47", "grey48"
)
grey3 <- c("grey49", "grey50", "grey51", "grey52", "grey53", 
           "grey54", "grey55", "grey56", "grey57", "grey58", 
           "grey59", "grey60", "grey61", "grey62", "grey63", 
           "grey64", "grey65", "grey66", "grey67", "grey68", 
           "grey69", "grey70", "grey71", "grey72", "grey73"
)
grey4 <- c("grey74", "grey75", "grey76", "grey77", "grey78", 
           "grey79", "grey80", "grey81", "grey82", "grey83", 
           "grey84", "grey85", "grey86", "grey87", "grey88", 
           "grey89", "grey90", "grey91", "grey92", "grey93"
)
grey5 <- c("grey94", "grey95", "grey96", "grey97", "grey98", 
           "grey99", "grey100"
)
show_col(grey1, cex_label = 0.6, ncol=5)
show_col(grey2, cex_label = 0.6, ncol=5)
show_col(grey3, cex_label = 0.6, ncol=5)
show_col(grey4, cex_label = 0.6, ncol=5)
show_col(grey5, cex_label = 0.6, ncol=5)
```

##### Offwhite

```{r, echo=FALSE}
offwhite1 <- c("antiquewhite", "antiquewhite1", "antiquewhite2", "antiquewhite3", "antiquewhite4", 
              "cornsilk", "cornsilk1", "cornsilk2", "cornsilk3", "cornsilk4",
              "ivory", "ivory1", "ivory2", "ivory3", "ivory4"
)
offwhite2 <- c("navajowhite", "navajowhite1","navajowhite2", "navajowhite3", "navajowhite4",
              "seashell", "seashell1", "seashell2", "seashell3", "seashell4", 
              "snow", "snow1", "snow2", "snow3", "snow4"
)
show_col(offwhite1, cex_label = 0.6, ncol=5)
show_col(offwhite2, cex_label = 0.6, ncol=5)
```



```{r include=FALSE}

randoms <- c("white", "floralwhite",  "ghostwhite", "mintcream", "whitesmoke", 
             "black",
             "aliceblue", "cornflowerblue", "darkblue", "darkcyan", "darkturquoise", 
             "mediumblue", "navy", "navyblue", "mediumturquoise", "midnightblue", "powderblue", 
             "beige",  "blanchedalmond", "papayawhip", "moccasin", "peru", "saddlebrown", "sandybrown",
             "blueviolet", "darkmagenta", "darkslateblue","darkviolet", "lavender", 
             "lightslateblue", "mediumslateblue", "mediumvioletred", "violet",
             "darkgray", "darkgrey", "dimgray", "dimgrey", "gainsboro", "lightgray",  
             "lightgrey", "lightslategray", "lightslategrey", "slategrey",
             "darkgreen", "forestgreen", "greenyellow",  "lawngreen", "lightgreen",
             "lightseagreen", "limegreen", "mediumaquamarine", "mediumseagreen",  "mediumspringgreen", "yellowgreen", 
             "darkkhaki", "darkred", "darksalmon", "darkslategrey", "lightcoral", "lightgoldenrodyellow", "linen", "oldlace",
             "palegoldenrod"
)

# Greens

greens <- c("aquamarine", "aquamarine1", "aquamarine2", "aquamarine3", "aquamarine4",
            "chartreuse", "chartreuse1", "chartreuse2", "chartreuse3", "chartreuse4",
            "darkolivegreen", "darkolivegreen1", "darkolivegreen2", "darkolivegreen3", "darkolivegreen4",
            "darkseagreen", "darkseagreen1", "darkseagreen2", "darkseagreen3", "darkseagreen4",
            "green", "green1", "green2", "green3", "green4",
            "honeydew", "honeydew1", "honeydew2", "honeydew3", "honeydew4",
            "olivedrab", "olivedrab1", "olivedrab2", "olivedrab3", "olivedrab4",
            "palegreen", "palegreen1", "palegreen2", "palegreen3", "palegreen4", 
            "seagreen", "seagreen1", "seagreen2", "seagreen3", "seagreen4",
            "springgreen", "springgreen1", "springgreen2", "springgreen3", "springgreen4"
)

# Blues

blues <- c("azure", "azure1", "azure2", "azure3", "azure4",
           "blue", "blue1", "blue2", "blue3", "blue4",
           "cadetblue", "cadetblue1", "cadetblue2", "cadetblue3", "cadetblue4",
           "cyan", "cyan1", "cyan2", "cyan3", "cyan4",
           "darkslategray", "darkslategray1", "darkslategray2", "darkslategray3", "darkslategray4",
           "deepskyblue", "deepskyblue1", "deepskyblue2", "deepskyblue3", "deepskyblue4",
           "dodgerblue", "dodgerblue1", "dodgerblue2", "dodgerblue3", "dodgerblue4",
           "lightblue", "lightblue1", "lightblue2", "lightblue3", "lightblue4", 
           "lightcyan", "lightcyan1", "lightcyan2", "lightcyan3", "lightcyan4",
           "lightskyblue", "lightskyblue1", "lightskyblue2", "lightskyblue3", "lightskyblue4",
           "lightsteelblue", "lightsteelblue1", "lightsteelblue2", "lightsteelblue3", "lightsteelblue4",
           "paleturquoise", "paleturquoise1", "paleturquoise2", "paleturquoise3", "paleturquoise4",
           "royalblue", "royalblue1", "royalblue2", "royalblue3", "royalblue4",
           "slategray", "slategray1", "slategray2", "slategray3", "slategray4",
           "skyblue", "skyblue1", "skyblue2", "skyblue3", "skyblue4",
           "steelblue", "steelblue1", "steelblue2", "steelblue3", "steelblue4",
           "turquoise", "turquoise1", "turquoise2", "turquoise3", "turquoise4"
)

# Browns

browns <- c("brown", "brown1", "brown2", "brown3", "brown4",
            "burlywood", "burlywood1", "burlywood2", "burlywood3", "burlywood4",
            "chocolate", "chocolate1", "chocolate2", "chocolate3", "chocolate4",
            "khaki", "khaki1", "khaki2", "khaki3", "khaki4",
            "sienna", "sienna1", "sienna2", "sienna3", "sienna4", 
            "tan", "tan1", "tan2", "tan3", "tan4",
            "wheat", "wheat1", "wheat2", "wheat3", "wheat4"
)

# Yellow

yellows <- c("darkgoldenrod", "darkgoldenrod1", "darkgoldenrod2", "darkgoldenrod3", "darkgoldenrod4",
             "gold", "gold1", "gold2", "gold3", "gold4", 
             "goldenrod", "goldenrod1", "goldenrod2", "goldenrod3", "goldenrod4",
             "lemonchiffon", "lemonchiffon1", "lemonchiffon2", "lemonchiffon3", "lemonchiffon4",
             "lightgoldenrod", "lightgoldenrod1", "lightgoldenrod2", "lightgoldenrod3", "lightgoldenrod4", 
             "lightyellow", "lightyellow1", "lightyellow2", "lightyellow3", "lightyellow4",
             "yellow", "yellow1", "yellow2", "yellow3", "yellow4"
)

# Orange

oranges <- c("bisque", "bisque1", "bisque2", "bisque3", "bisque4",
             "coral", "coral1", "coral2", "coral3", "coral4",
             "darkorange", "darkorange1", "darkorange2", "darkorange3", "darkorange4",
             "lightsalmon", "lightsalmon1", "lightsalmon2", "lightsalmon3", "lightsalmon4",
             "orange", "orange1", "orange2", "orange3", "orange4", 
             "orangered", "orangered1", "orangered2", "orangered3", "orangered4",
             "peachpuff", "peachpuff1", "peachpuff2", "peachpuff3", "peachpuff4",
             "salmon", "salmon1", "salmon2", "salmon3", "salmon4"
)

# Reds

reds <- c("firebrick", "firebrick1", "firebrick2", "firebrick3", "firebrick4",
          "indianred", "indianred1", "indianred2", "indianred3", "indianred4",
          "red", "red1", "red2", "red3", "red4",
          "tomato", "tomato1", "tomato2", "tomato3", "tomato4"
)

# Pinks

pinks <- c("deeppink", "deeppink1", "deeppink2", "deeppink3", "deeppink4",
           "hotpink", "hotpink1", "hotpink2", "hotpink3", "hotpink4",
           "lightpink", "lightpink1", "lightpink2", "lightpink3", "lightpink4",
           "mistyrose", "mistyrose1", "mistyrose2", "mistyrose3", "mistyrose4",
           "pink", "pink1", "pink2", "pink3", "pink4",
           "rosybrown", "rosybrown1", "rosybrown2", "rosybrown3", "rosybrown4",
           "violetred", "violetred1", "violetred2", "violetred3", "violetred4"
)

# Purples

purples <- c("darkorchid", "darkorchid1", "darkorchid2", "darkorchid3", "darkorchid4",
             "lavenderblush", "lavenderblush1", "lavenderblush2", "lavenderblush3", "lavenderblush4",
             "magenta", "magenta1", "magenta2", "magenta3", "magenta4", 
             "maroon", "maroon1", "maroon2", "maroon3", "maroon4", 
             "mediumorchid", "mediumorchid1", "mediumorchid2", "mediumorchid3", "mediumorchid4",
             "mediumpurple", "mediumpurple1", "mediumpurple2", "mediumpurple3", "mediumpurple4",
             "orchid", "orchid1", "orchid2", "orchid3", "orchid4", 
             "palevioletred", "palevioletred1", "palevioletred2", "palevioletred3", "palevioletred4",
             "purple", "purple1", "purple2", "purple3", "purple4",
             "plum", "plum1", "plum2", "plum3", "plum4",
             "slateblue", "slateblue1", "slateblue2", "slateblue3", "slateblue4",
             "thistle", "thistle1", "thistle2", "thistle3", "thistle4"
)

# Grey

grays <- c("gray", "gray0", "gray1", "gray2", "gray3",
           "gray4", "gray5", "gray6", "gray7", "gray8", 
           "gray9", "gray10", "gray11", "gray12",  "gray13",
           "gray14", "gray15", "gray16", "gray17", "gray18",
           "gray19", "gray20", "gray21", "gray22", "gray23",
           "gray24", "gray25", "gray26", "gray27", "gray28",
           "gray29", "gray30", "gray31", "gray32", "gray33", 
           "gray34", "gray35", "gray36", "gray37", "gray38",
           "gray39", "gray40", "gray41", "gray42", "gray43", 
           "gray44", "gray45", "gray46", "gray47", "gray48", 
           "gray49", "gray50", "gray51", "gray52", "gray53", 
           "gray54", "gray55", "gray56", "gray57", "gray58", 
           "gray59", "gray60", "gray61", "gray62", "gray63", 
           "gray64", "gray65", "gray66", "gray67", "gray68", 
           "gray69", "gray70", "gray71", "gray72", "gray73", 
           "gray74", "gray75", "gray76", "gray77", "gray78", 
           "gray79", "gray80", "gray81", "gray82", "gray83", 
           "gray84", "gray85", "gray86", "gray87", "gray88", 
           "gray89", "gray90", "gray91", "gray92", "gray93", 
           "gray94", "gray95", "gray96", "gray97", "gray98", 
           "gray99", "gray100"
)

greys <- c("grey", "grey0", "grey1", "grey2", "grey3", "grey4",
           "grey5", "grey6", "grey7", "grey8", "grey9", "grey10", 
           "grey11", "grey12", "grey13", "grey14", "grey15", "grey16", 
           "grey17", "grey18", "grey19", "grey20", "grey21", "grey22", 
           "grey23", "grey24", "grey25", "grey26", "grey27", "grey28", 
           "grey29", "grey30", "grey31", "grey32", "grey33", "grey34", 
           "grey35", "grey36", "grey37", "grey38", "grey39", "grey40",
           "grey41", "grey42", "grey43", "grey44", "grey45", "grey46", 
           "grey47", "grey48", "grey49", "grey50", "grey51", "grey52", 
           "grey53", "grey54", "grey55", "grey56", "grey57", "grey58", 
           "grey59", "grey60", "grey61", "grey62", "grey63", "grey64", 
           "grey65", "grey66", "grey67", "grey68", "grey69", "grey70", 
           "grey71", "grey72", "grey73", "grey74", "grey75", "grey76", 
           "grey77", "grey78", "grey79", "grey80", "grey81", "grey82", 
           "grey83", "grey84", "grey85", "grey86", "grey87", "grey88", 
           "grey89", "grey90", "grey91", "grey92", "grey93", "grey94", 
           "grey95", "grey96", "grey97", "grey98", "grey99", "grey100"
)

# Whites

offwhite <- c("antiquewhite", "antiquewhite1", "antiquewhite2", "antiquewhite3", "antiquewhite4", 
              "cornsilk", "cornsilk1", "cornsilk2", "cornsilk3", "cornsilk4",
              "ivory", "ivory1", "ivory2", "ivory3", "ivory4",
              "navajowhite", "navajowhite1","navajowhite2", "navajowhite3", "navajowhite4",
              "seashell", "seashell1", "seashell2", "seashell3", "seashell4", 
              "snow", "snow1", "snow2", "snow3", "snow4"
)

```

```{r include=FALSE}
a=data.frame(c=randoms, y=seq(0, length(randoms)-1)%%9, x=seq(0, length(randoms)-1)%/%9)
ggplot() +
scale_x_continuous(name="", breaks=NULL, expand=c(0, 0)) +
scale_y_continuous(name="", breaks=NULL, expand=c(0, 0)) +
scale_fill_identity() +
geom_rect(data=a, mapping=aes(xmin=x, xmax=x+1, ymin=y, ymax=y+1), fill="white") +
geom_rect(data=a, mapping=aes(xmin=x+0.05, xmax=x+1, ymin=y+0.5, ymax=y+1, fill=c)) +
geom_text(data=a, mapping=aes(x=x+0.5, y=y+0.5, label=c), colour="black", hjust=0.5, vjust=1.5, size=2.5)

```

